---
title: "CONSORT: Range Checks"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
source(file = file.path("prepare-analytic-datasets", "functions-for-analytical-dataset-creation.R"))  # Needed for the function 'convert_to_local_datetime'
```

```{r}
# These datasets contain data from only those sequences which began
# within the 10-day MRT period.
dat_matched_to_decision_points <- readRDS(file = file.path(path_manipulated_data, "dat_matched_to_decision_points.rds"))
dat_mars_time_varying_noise_reduction_vars <- readRDS(file = file.path(path_manipulated_data, "dat_mars_time_varying_noise_reduction_vars.rds"))
dat_mars_time_varying_moderators <- readRDS(file = file.path(path_manipulated_data, "dat_mars_time_varying_moderators.rds"))
# The following participants were excluded from all analyses:
# - Pilot participants
# - Among participants who have any data from sequences which began within the
#   10-day MRT period, those participants who did not complete
#   at least 3 EMA between the 2nd and 9th day inclusive.
mars_ids_excluded_from_all_analytic_datasets <- readRDS(file = file.path(path_manipulated_data, "mars_ids_excluded_from_all_analytic_datasets.rds"))
```

```{r}
# First, drop data from participants which we will not be using in any further
# analysis.
dat_matched_to_decision_points <- dat_matched_to_decision_points %>% filter(!(mars_id %in% mars_ids_excluded_from_all_analytic_datasets))
dat_matched_to_decision_points <- dat_matched_to_decision_points %>% 
  select(mars_id, decision_point, olson, A, block_number,
         ts_2qs_triggered_mountain, ts_status_survey_2qs_mountain,
         ts_coinflip_mountain, ts_ema_triggered_mountain, ts_status_survey_ema_mountain) %>%
  mutate(plot_no_group = 1)   # This variable was created to assist in plotting when we do not need to display summary statistics by group
```

```{r}
# Note that:
#   * dat_mars_time_varying_moderators is needed because of the column 'status_survey_ema_collapsed'
#   * dat_mars_time_varying_noise_reduction_vars is needed because of the column 'status_survey_2qs_collapsed'

dat_mars_analysis <- left_join(x = dat_mars_time_varying_moderators, 
                               y = dat_mars_time_varying_noise_reduction_vars,
                               by = join_by(mars_id == mars_id,
                                            decision_point == decision_point))
dat_mars_analysis <- left_join(x = dat_mars_analysis, 
                               y = dat_matched_to_decision_points,
                               by = join_by(mars_id == mars_id,
                                            decision_point == decision_point))
```

```{r}
# Next, drop sequences which occur on the first day or last day of the MRT
dat_mars_analysis <- dat_mars_analysis %>% filter((decision_point >= 7) & (decision_point <= 54))
```

```{r}
n_participants <- length(unique(dat_mars_analysis[["mars_id"]]))
n_blocks <- nrow(dat_mars_analysis)
n_rand <- sum(!is.na(dat_mars_analysis[["ts_coinflip_mountain"]]))
```

We used `r n_participants` participants and `r n_blocks` person-blocks to conduct checks described in this document. These `r n_blocks` person-blocks had `r n_rand` micro-randomizations, i.e., participants were eligible for micro-randomization in about 81% of the `r n_blocks` person-blocks.

```{r}
dat_mars_analysis[["ts_2qs_triggered_local"]] <- convert_to_local_datetime(cleaned_data_frame = dat_mars_analysis, datetime_mountain_name = "ts_2qs_triggered_mountain")
dat_mars_analysis[["ts_status_survey_2qs_local"]] <- convert_to_local_datetime(cleaned_data_frame = dat_mars_analysis, datetime_mountain_name = "ts_status_survey_2qs_mountain")
dat_mars_analysis[["ts_coinflip_local"]] <- convert_to_local_datetime(cleaned_data_frame = dat_mars_analysis, datetime_mountain_name = "ts_coinflip_mountain")
dat_mars_analysis[["ts_ema_triggered_local"]] <- convert_to_local_datetime(cleaned_data_frame = dat_mars_analysis, datetime_mountain_name = "ts_ema_triggered_mountain")
dat_mars_analysis[["ts_status_survey_ema_local"]] <- convert_to_local_datetime(cleaned_data_frame = dat_mars_analysis, datetime_mountain_name = "ts_status_survey_ema_mountain")
```

```{r}
dat_mars_analysis <- dat_mars_analysis %>% filter(!is.na(ts_2qs_triggered_mountain))
```

```{r}
list_quants <- list()
```

# Check: Minutes elapsed between when brief survey was administered and when brief survey was completed

```{r}
# Note that you need to take only the subset of the data for which brief survey 
# was completed prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(status_survey_2qs_collapsed == "fully_completed") %>% filter(status_survey_2qs_collapsed == "fully_completed") %>% filter(!is.na(ts_status_survey_2qs_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_2qs_triggered_local"]] %--% dat_for_calculation[["ts_status_survey_2qs_local"]])/(60)  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(Q1 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")

g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0,5)) + scale_x_continuous("", labels = NULL, breaks = NULL)
ggsave(filename = file.path("check-conditions", "plots", "Q1.png"), height = 10, width = 3, units = "in")
```

# Check: Minutes elapsed between when brief survey was administered and when micro-randomization occurred

```{r}
# Note that you need to take only the subset of the data for which micro-randomization
# occurred prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(!is.na(ts_coinflip_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_2qs_triggered_local"]] %--% dat_for_calculation[["ts_coinflip_local"]])/(60)  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(Q2 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")
 
g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0,140), breaks = seq(0,140,20), labels = seq(0,140,20)) + scale_x_continuous("", labels = NULL, breaks = NULL)
ggsave(filename = file.path("check-conditions", "plots", "Q2.png"), height = 10, width = 3, units = "in")
```

# Check: Minutes elapsed between when brief survey was administered and when EMA was administered

```{r}
# Note that you need to take only the subset of the data for which micro-randomization
# occurred prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(!is.na(ts_ema_triggered_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_2qs_triggered_local"]] %--% dat_for_calculation[["ts_ema_triggered_local"]])/(60)  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(Q3 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")
 
g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0, 140), breaks = seq(0,140,20), labels = seq(0,140,20)) + scale_x_continuous("", labels = NULL, breaks = NULL)
ggsave(filename = file.path("check-conditions", "plots", "Q3.png"), height = 10, width = 3, units = "in")
```

# Check: Minutes elapsed between when EMA was administered and when EMA was completed

```{r}
# Note that you need to take only the subset of the data for which micro-randomization
# occurred prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(!is.na(ts_ema_triggered_local)) %>% filter(status_survey_ema_collapsed == "fully_completed") %>% filter(!is.na(ts_status_survey_ema_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_ema_triggered_local"]] %--% dat_for_calculation[["ts_status_survey_ema_local"]])/(60)  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(Q4 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")
 
g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0, 140), breaks = seq(0,140,20), labels = seq(0,140,20)) + scale_x_continuous("", labels = NULL, breaks = NULL)
ggsave(filename = file.path("check-conditions", "plots", "Q4.png"), height = 10, width = 3, units = "in")
```

# Check: Minutes elapsed between when brief survey was completed and micro-randomization

```{r}
# Note that you need to take only the subset of the data for which brief survey 
# was completed prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(status_survey_2qs_collapsed == "fully_completed") %>% filter(status_survey_2qs_collapsed == "fully_completed") %>% filter(!is.na(ts_status_survey_2qs_local)) %>% filter(!is.na(ts_coinflip_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_status_survey_2qs_local"]] %--% dat_for_calculation[["ts_coinflip_local"]])/60  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(R1 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")

quantile(dat_for_calculation[["elapsed_mins"]], c(0, 0.25, 0.50, 0.75, seq(0.90, 1, 0.01))) 

g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0, 60), breaks = seq(0,60,20), labels = seq(0,60,20)) + scale_x_continuous("", labels = NULL, breaks = NULL)
ggsave(filename = file.path("check-conditions", "plots", "R1.png"), height = 10, width = 3, units = "in")
```

# Check: Minutes elapsed between when micro-randomization occurred and when EMA was completed

```{r}
# Note that you need to take only the subset of the data for which micro-randomization
# occurred prior to performing this calculation
dat_for_calculation <- dat_mars_analysis %>% filter(!is.na(ts_ema_triggered_local)) %>% filter(status_survey_ema_collapsed == "fully_completed") %>% filter(!is.na(ts_status_survey_ema_local)) %>% filter(!is.na(ts_coinflip_local))
dat_for_calculation[["elapsed_mins"]] <- int_length(dat_for_calculation[["ts_coinflip_local"]] %--% dat_for_calculation[["ts_status_survey_ema_local"]])/(60)  # Minutes

quants <- quantile(dat_for_calculation[["elapsed_mins"]]) 
list_quants <- append(list_quants, list(R2 = quants))
quants %>% kable(., digits = 3, col.names = "Percentiles of mins elapsed")
 
g <- ggplot(data = dat_for_calculation, aes(x = plot_no_group, y = elapsed_mins))
g + geom_violin(scale = "area", color = "cyan4", linewidth = 1) + geom_boxplot(color = "black", fill = "goldenrod", linewidth = 0.7, width = 0.10) + scale_y_continuous("Minutes Elapsed", limits = c(0, 160), breaks = seq(0,160,20), labels = seq(0,160,20)) + scale_x_continuous("", labels = NULL, breaks = NULL) + geom_abline(slope = 0, intercept = 140, color = "red", linewidth = 1)
ggsave(filename = file.path("check-conditions", "plots", "R2.png"), height = 10, width = 3, units = "in")
```

```{r}
dat_quants <- bind_cols(list_quants)
row.names(dat_quants) <- c("Minimum", "25th-Percentile", "50th-Percentile", "75th-Percentile", "Maximum")
write.csv(dat_quants, file.path("check-conditions", "plots", "checks_quantiles_minutes_elapsed.csv"), row.names = TRUE)
```

# Checks: Empirical randomization probabilities

```{r}
dat_for_calculation <- dat_mars_analysis %>% filter(!is.na(ts_coinflip_local))

dat_summary <- dat_for_calculation %>%
  summarise(n_none = sum(A == "none"),
            n_low_effort = sum(A == "low_effort"),
            n_mars = sum(A == "mars"),
            n_total_rand = n()) %>%
  mutate(prop_none = n_none/n_total_rand,
         prop_low_effort = n_low_effort/n_total_rand,
         prop_mars = n_mars/n_total_rand) %>%
  mutate(n_total_prop = prop_none + prop_low_effort + prop_mars) %>%
  mutate(prop_none_LB95 = prop_none - qnorm(0.975)*sqrt(prop_none*(1-prop_none))*sqrt(1/n_none),
         prop_none_UB95 = prop_none + qnorm(0.975)*sqrt(prop_none*(1-prop_none))*sqrt(1/n_none)) %>%
  mutate(prop_low_effort_LB95 = prop_low_effort - qnorm(0.975)*sqrt(prop_low_effort*(1-prop_low_effort))*sqrt(1/n_low_effort),
         prop_low_effort_UB95 = prop_low_effort + qnorm(0.975)*sqrt(prop_low_effort*(1-prop_low_effort))*sqrt(1/n_low_effort)) %>%
  mutate(prop_mars_LB95 = prop_mars - qnorm(0.975)*sqrt(prop_mars*(1-prop_mars))*sqrt(1/n_mars),
         prop_mars_UB95 = prop_mars + qnorm(0.975)*sqrt(prop_mars*(1-prop_mars))*sqrt(1/n_mars))

dat_randprob_95ci <- data.frame(treatment = c("none", "low effort", "high effort", "total"),
                                count_randomizations = c(dat_summary[["n_none"]], dat_summary[["n_low_effort"]], dat_summary[["n_mars"]], dat_summary[["n_total_rand"]]),
                                est_prob = c(dat_summary[["prop_none"]], dat_summary[["prop_low_effort"]], dat_summary[["prop_mars"]], dat_summary[["n_total_prop"]]),
                                LB95 = c(dat_summary[["prop_none_LB95"]], dat_summary[["prop_low_effort_LB95"]], dat_summary[["prop_mars_LB95"]], NA),
                                UB95 = c(dat_summary[["prop_none_UB95"]], dat_summary[["prop_low_effort_UB95"]], dat_summary[["prop_mars_UB95"]], NA))
```

```{r}
options(knitr.kable.NA = '')
dat_randprob_95ci %>% kable(., digits = 3)
```

```{r}
dat_summary_reshaped <- data.frame(A = c("none", "low effort prompt", "high effort prompt"),
                                   est = c(dat_summary$prop_none, dat_summary$prop_low_effort, dat_summary$prop_mars),
                                   LB95 = c(dat_summary$prop_none_LB95,dat_summary$prop_low_effort_LB95,dat_summary$prop_mars_LB95),
                                   UB95 = c(dat_summary$prop_none_UB95,dat_summary$prop_low_effort_UB95,dat_summary$prop_mars_UB95))

g <- ggplot(data = dat_summary_reshaped, aes(x = A, y = est, ymin = LB95, ymax = UB95, group = A))
g + geom_errorbar(width = 0.10) + geom_point(size=4, shape=21, fill="white") + scale_y_continuous(limits = c(0,1), name = "Empirical randomization probability and 95% CI's") + geom_abline(slope = 0, intercept = 0.50, color = "red", linewidth = 1) + geom_abline(slope = 0, intercept = 0.25, color = "red", linewidth = 1) + scale_x_discrete(name = "Randomization assignment")

ggsave(filename = file.path("check-conditions", "plots", "rand.png"), height = 10, width = 4, units = "in")
```

```{r}
dat_summary <- dat_for_calculation %>%
  group_by(block_number) %>%
  summarise(n_none = sum(A == "none"),
            n_low_effort = sum(A == "low_effort"),
            n_mars = sum(A == "mars"),
            n_total_rand = n()) %>%
  mutate(prop_none = n_none/n_total_rand,
         prop_low_effort = n_low_effort/n_total_rand,
         prop_mars = n_mars/n_total_rand) %>%
  mutate(n_total_prop = prop_none + prop_low_effort + prop_mars) %>%
  mutate(prop_none_LB95 = prop_none - qnorm(0.975)*sqrt(prop_none*(1-prop_none))*sqrt(1/n_none),
         prop_none_UB95 = prop_none + qnorm(0.975)*sqrt(prop_none*(1-prop_none))*sqrt(1/n_none)) %>%
  mutate(prop_low_effort_LB95 = prop_low_effort - qnorm(0.975)*sqrt(prop_low_effort*(1-prop_low_effort))*sqrt(1/n_low_effort),
         prop_low_effort_UB95 = prop_low_effort + qnorm(0.975)*sqrt(prop_low_effort*(1-prop_low_effort))*sqrt(1/n_low_effort)) %>%
  mutate(prop_mars_LB95 = prop_mars - qnorm(0.975)*sqrt(prop_mars*(1-prop_mars))*sqrt(1/n_mars),
         prop_mars_UB95 = prop_mars + qnorm(0.975)*sqrt(prop_mars*(1-prop_mars))*sqrt(1/n_mars))

dat_randprob_95ci <- data.frame(treatment = c(rep("none", 6), rep("low effort", 6), rep("high effort", 6), rep("total", 6)),
                                block = rep(0:5, times = 4),
                                count_randomizations = c(dat_summary[["n_none"]], dat_summary[["n_low_effort"]], dat_summary[["n_mars"]], dat_summary[["n_total_rand"]]),
                                est_prob = c(dat_summary[["prop_none"]], dat_summary[["prop_low_effort"]], dat_summary[["prop_mars"]], dat_summary[["n_total_prop"]]),
                                LB95 = c(dat_summary[["prop_none_LB95"]], dat_summary[["prop_low_effort_LB95"]], dat_summary[["prop_mars_LB95"]], rep(NA, 6)),
                                UB95 = c(dat_summary[["prop_none_UB95"]], dat_summary[["prop_low_effort_UB95"]], dat_summary[["prop_mars_UB95"]], rep(NA, 6)))
```

```{r}
options(knitr.kable.NA = '')
dat_randprob_95ci %>% kable(., digits = 3)
```

```{r}
dat_summary <- dat_summary %>% mutate(block_number = block_number + 1)
dat1 <- dat_summary %>% filter(block_number == 1)
dat2 <- dat_summary %>% filter(block_number == 2)
dat3 <- dat_summary %>% filter(block_number == 3)
dat4 <- dat_summary %>% filter(block_number == 4)
dat5 <- dat_summary %>% filter(block_number == 5)
dat6 <- dat_summary %>% filter(block_number == 6)
dat_all_blocks <- rbind(dat1, dat2, dat3, dat4, dat5, dat6)
```

```{r}
g <- ggplot(data = dat_all_blocks, aes(x = block_number, y = prop_none, group = block_number, ymin = prop_none_LB95, ymax = prop_none_UB95))
g + geom_errorbar() + geom_point(size=4, shape=21, fill="white") + scale_y_continuous(limits = c(0,1), name = "Empirical randomization probability and 95% CI's") + geom_abline(slope = 0, intercept = 0.50, color = "red", linewidth = 1) + scale_x_continuous(name = "Day-Level Block Order", breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6))

ggsave(filename = file.path("check-conditions", "plots", "rand_no_prompt_by_block.png"), height = 10, width = 3, units = "in")
```

```{r}
g <- ggplot(data = dat_all_blocks, aes(x = block_number, y = prop_low_effort, group = block_number, ymin = prop_low_effort_LB95, ymax = prop_low_effort_UB95))
g + geom_errorbar() + geom_point(size=4, shape=21, fill="white") + scale_y_continuous(limits = c(0,1), name = "Empirical randomization probability and 95% CI's") + geom_abline(slope = 0, intercept = 0.25, color = "red", linewidth = 1) + scale_x_continuous(name = "Day-Level Block Order", breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6))

ggsave(filename = file.path("check-conditions", "plots", "rand_low_effort_prompt_by_block.png"), height = 10, width = 3, units = "in")
```

```{r}
g <- ggplot(data = dat_all_blocks, aes(x = block_number, y = prop_mars, group = block_number, ymin = prop_mars_LB95, ymax = prop_mars_UB95))
g + geom_errorbar() + geom_point(size=4, shape=21, fill="white") + scale_y_continuous(limits = c(0,1), name = "Empirical randomization probability and 95% CI's") + geom_abline(slope = 0, intercept = 0.25, color = "red", linewidth = 1) + scale_x_continuous(name = "Day-Level Block Order", breaks = c(1,2,3,4,5,6), labels = c(1,2,3,4,5,6))

ggsave(filename = file.path("check-conditions", "plots", "rand_high_effort_prompt_by_block.png"), height = 10, width = 3, units = "in")
```

