---
title: "MARS MRT: H1 and Exploratory Analyses on Moderated Effect of Time"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
library(MRTAnalysis)
```

```{r}
is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output"))
}

is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output", "H1"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output", "H1"))
}
```

```{r}
# This is the data frame that is the output of the very last step of our data pipeline
dat_primary_aim <- readRDS(file = file.path(path_manipulated_data, "dat_primary_aim.rds")) 
```

```{r}
dat_primary_aim <- dat_primary_aim %>%
  mutate(is_include_main = if_else((decision_point >= 7) & (decision_point <= 54), 1, 0),    # Drop the first 6 and last 6 decision points
         is_include_sensitivity = 1)                                                         # Keep all decision points
```

**H1 Main Analysis** excludes first and last days of the 10-day MRT while **H1 Sensitivity Analysis** includes all days of the 10-day MRT. In **Exploratory Analysis on Moderated Effect of Time**, we investigate whether the effect of prompt (versus no prompt) varies by day in study, where day in study is modeled in a linear or quadratic manner.

# H1 Main Analysis 

```{r}
dat_for_analysis <- dat_primary_aim %>%
  filter(is_include_main == 1) %>%
  select(participant_id, decision_point, eligibility, 
         coinflip,
         Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val)
```

## Estimated prevalence by group (marginal over time)

```{r}
dat_prevalence <- dat_for_analysis %>%
  filter(eligibility == 1) %>%
  group_by(coinflip) %>%
  summarise(mu_Y = mean(Y, na.rm = TRUE)) %>%
  arrange(desc(coinflip))

dat_prevalence
```

```{r}
# Format output to 3 decimal places
dat_prevalence %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "prevalence_by_group_H1.csv"), row.names = TRUE)
```

```{r, fig.width = 4, fig.height = 8}
dat_prevalence %>%
  arrange(mu_Y) %>%
  mutate(coinflip_factor = if_else(coinflip == 0, "No Prompt", "Prompt")) %>%
  mutate(coinflip_factor = as_factor(coinflip_factor)) %>%
  ggplot(aes(x = coinflip_factor, y = mu_Y)) + geom_bar(stat="identity", color="black", fill="#56B4E9", size = 2) + scale_x_discrete(name="Treatment Assignment") + scale_y_continuous(name="Proportion engaged with self-regulatory strategies ~1 hour after micro-randomization", limits=c(0,1), breaks = seq(0,1,0.10)) + theme(legend.position = "none") + geom_text(aes(label=round(mu_Y, 2)), vjust=-0.3, size=6)

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "prevalence.png"), dpi = 1200)
```

```{r}
my_list <- list(Y = -1,
                coinflip = -1,
                hour_coinflip_local = -1, 
                days_between_v1_and_coinflip_local = -1,
                any_response_2qs = -1, 
                any_recent_eligible_dp = -1, 
                engagement_most_recent_eligible = -1,
                age = -1, 
                is_male = -1, 
                is_latino = -1, 
                is_not_latino_and_black = -1, 
                is_not_latino_and_other = -1, 
                baseline_tobacco_history = -1, 
                has_partner = -1, 
                income_val = -1)
```

```{r}
logical_vec_cc <- dat_for_analysis %>%
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other,
         baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)

dat_summary_observed <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1) %>%
  group_by(is_complete) %>%
  summarise(total = n())

n_participants_included_among_elig <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1 & is_complete == 1) %>% 
  summarise(total = length(unique(participant_id))) %>%
  .[["total"]]

n_participants_elig <- dat_for_analysis %>%
  filter(eligibility == 1) %>%
  .[["participant_id"]] %>%
  unique(.) %>%
  length(.)

n_participants_excluded_among_elig <- n_participants_elig - n_participants_included_among_elig

dat_summary <- data.frame(n_participants_elig = n_participants_elig,
                          n_participants_included_among_elig = n_participants_included_among_elig,
                          n_participants_excluded_among_elig = n_participants_excluded_among_elig,
                          n_blocks_elig = sum(dat_summary_observed[["total"]]),
                          n_blocks_included_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == TRUE, ][["total"]],
                          n_blocks_excluded_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == FALSE, ][["total"]])

dat_summary
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
participants_fully_dropped <- dat_for_analysis %>% 
  group_by(participant_id) %>% 
  summarise(count_elig = sum(eligibility)) %>%
  arrange(count_elig) %>%
  filter(count_elig == 0) %>%
  .[["participant_id"]]

if(length(participants_fully_dropped) > 0){
  dat_for_analysis <- dat_for_analysis %>% filter(!(participant_id %in% participants_fully_dropped))
}
```

## Estimated effect on the log risk ratio scale

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit1, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1.csv"), row.names = TRUE)
```

## Estimated effect on the risk ratio scale

```{r}
# Present results on the risk ratio scale
significance_level <- 0.05
n_terms_causal <- fit1$fit$dims$p
n_terms_control <- fit1$fit$dims$q
n_terms_total <- n_terms_causal + n_terms_control
degrees_of_freedom <- n_participants_included_among_elig - n_terms_causal - n_terms_control
critical_value <- qt(1 - significance_level/2, df = degrees_of_freedom)

est_beta <- as.matrix(fit1$fit$beta_hat)
est_covmat_beta <- fit1$fit$varcov_adjusted[(n_terms_control + 1):n_terms_total,(n_terms_control + 1):n_terms_total]

exp_estimates <- exp(est_beta)
var_rr <- (exp_estimates) %*% est_covmat_beta %*% t(exp_estimates)
stderr_rr <- sqrt(var_rr)
rrLB95 <- exp_estimates - critical_value * stderr_rr
rrUB95 <- exp_estimates + critical_value * stderr_rr

dat_exp_scale <- data.frame(exp_estimates = exp_estimates, stderr_rr = c(stderr_rr), rrLB95 = c(rrLB95), rrUB95 = c(rrUB95))

dat_exp_scale
```

```{r}
# Format output to 3 decimal places
dat_exp_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "risk_ratio_scale_H1.csv"), row.names = TRUE)
```

## Estimated effect on the risk difference scale

```{r}
fit1 <- wcls(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit1, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "risk_difference_scale_H1.csv"), row.names = TRUE)
```

# Exploratory Analysis (Linear Effect of Time)

## Day in study

```{r}
fit2 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ days_between_v1_and_coinflip_local,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit2, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit2, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit2, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_linear_day.csv"), row.names = TRUE)
```

```{r, fig.width = 8, fig.height = 12}
Lmat <- matrix(c(rep(1,8), seq(2,9,1)), byrow = FALSE, ncol = 2)
dat_result_for_plotting <- summary(fit2, show_control_fit = FALSE, lincomb = Lmat)[["causal_excursion_effect"]]
dat_result_for_plotting <- dat_result_for_plotting[-c(1,2),]
dat_result_for_plotting <- as.data.frame(dat_result_for_plotting)
dat_result_for_plotting$days_since_start <- 2:9

dat_result_for_plotting %>% 
  ggplot(aes(x=days_since_start, y=Estimate, color="red")) + geom_hline(yintercept=0, linetype=1, color = "black", size=1) + geom_point(size = 2) + geom_line(linewidth=1) + geom_ribbon(aes(ymin=`95% LCL`, ymax=`95% UCL`), linetype=3, linewidth=1, alpha=0.2) + scale_x_continuous(name="Day (t)", limits=c(2, 9), breaks = seq(2,9,1)) + scale_y_continuous(name="Estimate on log scale", limits=c(-1.5,1.0), breaks = seq(-1.5,1.0,0.10)) + theme(legend.position = "none") 

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_linear.png"), dpi = 1200)
```

```{r, fig.width = 8, fig.height = 12}
Lmat <- matrix(c(rep(1,8), seq(2,9,1)), byrow = FALSE, ncol = 2)
dat_result_for_plotting <- summary(fit2, show_control_fit = FALSE, lincomb = Lmat)[["causal_excursion_effect"]]
dat_result_for_plotting <- dat_result_for_plotting[-c(1,2),]
dat_result_for_plotting <- as.data.frame(dat_result_for_plotting)
dat_result_for_plotting$Estimate <- exp(dat_result_for_plotting$Estimate)
dat_result_for_plotting$`95% LCL` <- exp(dat_result_for_plotting$`95% LCL`)
dat_result_for_plotting$`95% UCL` <- exp(dat_result_for_plotting$`95% UCL`)
dat_result_for_plotting$days_since_start <- 2:9

dat_result_for_plotting %>% 
  ggplot(aes(x=days_since_start, y=Estimate, color="red")) + geom_hline(yintercept=1, linetype=1, color = "black", size=1) + geom_point(size = 2) + geom_line(linewidth=1) + geom_ribbon(aes(ymin=`95% LCL`, ymax=`95% UCL`), linetype=3, linewidth=1, alpha=0.2) + scale_x_continuous(name="Day (t)", limits=c(2,9), breaks = seq(2,9,1)) + scale_y_continuous(name="Estimate on risk ratio scale", limits=c(0,2), breaks = seq(0,2,0.10)) + theme(legend.position = "none") 

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "risk_ratio_scale_H1_linear.png"), dpi = 1200)
```

```{r, fig.width = 8, fig.height = 6}
dat_result_for_plotting %>% 
  ggplot(aes(x=days_since_start, y=Estimate, color="red")) + geom_hline(yintercept=1, linetype=1, color = "black", size=2) + geom_point(size = 4) + geom_line(linewidth=2) + geom_ribbon(aes(ymin=`95% LCL`, ymax=`95% UCL`), linetype=3, linewidth=2, alpha=0.2) + scale_x_continuous(name="Day (t)", limits=c(2,9), breaks = seq(2,9,1)) + scale_y_continuous(name="Estimate on risk ratio scale", limits=c(0.7,1.5), breaks = seq(0.7,1.5,0.10)) + theme(legend.position = "none") 

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "zoomed_risk_ratio_scale_H1_linear.png"), dpi = 1200)
```

## Hour of day

```{r}
fit2 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ hour_coinflip_local,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit2, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit2, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit2, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_linear_hour.csv"), row.names = TRUE)
```

# Exploratory Analysis (Quadratic Effect of Time)

## Day in study

```{r}
fit3 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ days_between_v1_and_coinflip_local + I(days_between_v1_and_coinflip_local * days_between_v1_and_coinflip_local),  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + I(days_between_v1_and_coinflip_local * days_between_v1_and_coinflip_local) + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit3, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit3, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit3, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_quadratic_day.csv"), row.names = TRUE)
```

```{r, fig.width = 8, fig.height = 12}
Lmat <- matrix(c(rep(1,8), seq(2,9,1), seq(2,9,1)), byrow = FALSE, ncol = 3)
dat_result_for_plotting <- summary(fit3, show_control_fit = FALSE, lincomb = Lmat)[["causal_excursion_effect"]]
dat_result_for_plotting <- dat_result_for_plotting[-c(1:3),]
dat_result_for_plotting <- as.data.frame(dat_result_for_plotting)
dat_result_for_plotting$days_since_start <- 2:9

dat_result_for_plotting %>% 
  ggplot(aes(x=days_since_start, y=Estimate, color="red")) + geom_hline(yintercept=0, linetype=1, color = "black", size=1) + geom_point(size = 2) + geom_line(linewidth=1) + geom_ribbon(aes(ymin=`95% LCL`, ymax=`95% UCL`), linetype=3, linewidth=1, alpha=0.2) + scale_x_continuous(name="Day (t)", limits=c(2, 9), breaks = seq(2,9,1)) + scale_y_continuous(name="Estimate on log scale", limits=c(-1.5,1.0), breaks = seq(-1.5,1.0,0.10)) + theme(legend.position = "none") 

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_quadratic.png"), dpi = 1200)
```

```{r, fig.width = 8, fig.height = 12}
Lmat <- matrix(c(rep(1,8), seq(2,9,1), seq(2,9,1)), byrow = FALSE, ncol = 3)
dat_result_for_plotting <- summary(fit3, show_control_fit = FALSE, lincomb = Lmat)[["causal_excursion_effect"]]
dat_result_for_plotting <- dat_result_for_plotting[-c(1:3),]
dat_result_for_plotting <- as.data.frame(dat_result_for_plotting)
dat_result_for_plotting$Estimate <- exp(dat_result_for_plotting$Estimate)
dat_result_for_plotting$`95% LCL` <- exp(dat_result_for_plotting$`95% LCL`)
dat_result_for_plotting$`95% UCL` <- exp(dat_result_for_plotting$`95% UCL`)
dat_result_for_plotting$days_since_start <- 2:9

dat_result_for_plotting %>% 
  ggplot(aes(x=days_since_start, y=Estimate, color="red")) + geom_hline(yintercept=1, linetype=1, color = "black", size=1) + geom_point(size = 2) + geom_line(linewidth=1) + geom_ribbon(aes(ymin=`95% LCL`, ymax=`95% UCL`), linetype=3, linewidth=1, alpha=0.2) + scale_x_continuous(name="Day (t)", limits=c(2,9), breaks = seq(2,9,1)) + scale_y_continuous(name="Estimate on risk ratio scale", limits=c(0,2), breaks = seq(0,2,0.10)) + theme(legend.position = "none") 

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "H1", "risk_ratio_scale_H1_quadratic.png"), dpi = 1200)
```

## Hour of day

```{r}
fit3 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ hour_coinflip_local + I(hour_coinflip_local * hour_coinflip_local),  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + I(hour_coinflip_local * hour_coinflip_local) + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit3, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit3, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit3, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "log_risk_ratio_scale_H1_quadratic_hour.csv"), row.names = TRUE)
```

# H1 Sensitivity Analysis

```{r}
dat_for_analysis <- dat_primary_aim %>%
  filter(is_include_sensitivity == 1) %>%
  select(participant_id, decision_point, eligibility, 
         coinflip,
         Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val)
```

## Estimated prevalence by group

```{r}
dat_prevalence <- dat_for_analysis %>%
  filter(eligibility == 1) %>%
  group_by(coinflip) %>%
  summarise(mu_Y = mean(Y, na.rm = TRUE)) %>%
  arrange(desc(coinflip))

dat_prevalence
```

```{r}
# Format output to 3 decimal places
dat_prevalence %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "sensitivity_prevalence_by_group_H1.csv"), row.names = TRUE)
```

```{r}
my_list <- list(Y = -1,
                coinflip = -1,
                hour_coinflip_local = -1, 
                days_between_v1_and_coinflip_local = -1,
                any_response_2qs = -1, 
                any_recent_eligible_dp = -1, 
                engagement_most_recent_eligible = -1,
                age = -1, 
                is_male = -1, 
                is_latino = -1, 
                is_not_latino_and_black = -1, 
                is_not_latino_and_other = -1, 
                baseline_tobacco_history = -1, 
                has_partner = -1, 
                income_val = -1)
```

```{r}
logical_vec_cc <- dat_for_analysis %>%
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other,
         baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)

dat_summary_observed <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1) %>%
  group_by(is_complete) %>%
  summarise(total = n())

n_participants_included_among_elig <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1 & is_complete == 1) %>% 
  summarise(total = length(unique(participant_id))) %>%
  .[["total"]]

n_participants_elig <- dat_for_analysis %>%
  filter(eligibility == 1) %>%
  .[["participant_id"]] %>%
  unique(.) %>%
  length(.)

n_participants_excluded_among_elig <- n_participants_elig - n_participants_included_among_elig

dat_summary <- data.frame(n_participants_elig = n_participants_elig,
                          n_participants_included_among_elig = n_participants_included_among_elig,
                          n_participants_excluded_among_elig = n_participants_excluded_among_elig,
                          n_blocks_elig = sum(dat_summary_observed[["total"]]),
                          n_blocks_included_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == TRUE, ][["total"]],
                          n_blocks_excluded_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == FALSE, ][["total"]])

dat_summary
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
participants_fully_dropped <- dat_for_analysis %>% 
  group_by(participant_id) %>% 
  summarise(count_elig = sum(eligibility)) %>%
  arrange(count_elig) %>%
  filter(count_elig == 0) %>%
  .[["participant_id"]]

if(length(participants_fully_dropped) > 0){
  dat_for_analysis <- dat_for_analysis %>% filter(!(participant_id %in% participants_fully_dropped))
}
```

## Estimated effect on the log risk ratio scale

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit1, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "sensitivity_log_risk_ratio_scale_H1.csv"), row.names = TRUE)
```

```{r}
# Present results on the risk ratio scale
significance_level <- 0.05
n_terms_causal <- fit1$fit$dims$p
n_terms_control <- fit1$fit$dims$q
n_terms_total <- n_terms_causal + n_terms_control
degrees_of_freedom <- n_participants_included_among_elig - n_terms_causal - n_terms_control
critical_value <- qt(1 - significance_level/2, df = degrees_of_freedom)

est_beta <- as.matrix(fit1$fit$beta_hat)
est_covmat_beta <- fit1$fit$varcov_adjusted[(n_terms_control + 1):n_terms_total,(n_terms_control + 1):n_terms_total]

exp_estimates <- exp(est_beta)
var_rr <- (exp_estimates) %*% est_covmat_beta %*% t(exp_estimates)
stderr_rr <- sqrt(var_rr)
rrLB95 <- exp_estimates - critical_value * stderr_rr
rrUB95 <- exp_estimates + critical_value * stderr_rr

dat_exp_scale <- data.frame(exp_estimates = exp_estimates, stderr_rr = c(stderr_rr), rrLB95 = c(rrLB95), rrUB95 = c(rrUB95))

dat_exp_scale
```

```{r}
# Format output to 3 decimal places
dat_exp_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "sensitivity_risk_ratio_scale_H1.csv"), row.names = TRUE)
```

## Estimated effect on the risk difference scale

```{r}
fit1 <- wcls(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_male + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

```{r}
dat_result_causal <- summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]]
dat_result_control <- summary(fit1, show_control_fit = TRUE)[["control_variables"]]

dat_result <- rbind(dat_result_causal, dat_result_control)

# Format output to 3 decimal places
dat_result %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1", "sensitivity_risk_difference_scale_H1.csv"), row.names = TRUE)
```

```{r}
if(file.exists("analysis-complete-case/formatted-output/H1/Thumbs.db")){
  file.remove("analysis-complete-case/formatted-output/H1/Thumbs.db")
}
```
