---
title: "MARS MRT: H3"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>
```
```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
library(MRTAnalysis)
```

Let $X_t$ denote the observed value of any of the constructs listed below at decision point $t$, $I_t$ denote an indicator for whether decision point $t$ was eligible for micro-randomization, and $n_t$ denote the total number of eligible decision points within the past 24 hours prior to $t$ (not including $t$ itself). We consider three ways to operationalize constructs listed below:

-   **(value at prior decision point)** value in the decision point prior to the current decision point, i.e., $X_{t-1}$ given that $I_{t-1}=1$

-   **(mean within past 24 hours)** mean over all eligible decision points in the past 24 hours prior to the current decision point, i.e., $\frac{1}{\sum_{j=1}^{n_t}I_{t-j}} \sum_{j=1}^{n_t} X_{t-j} I_{t-j}$ given that $\sum_{j=1}^{n_t}I_{t-j} \geq 1$

-   **(sum within past 24 hours)** sum over all eligible decision points in the past 24 hours prior to the current decision point, i.e., $\sum_{j=1}^{n_t} X_{t-j} I_{t-j}$ given that given that $\sum_{j=1}^{n_t}I_{t-j} \geq 1$

| Construct                              | Operationalization #1         | Operationalization #2     |
|----------------------------------------|-------------------------------|---------------------------|
| Ashamed                                | value at prior decision point | mean within past 24 hours |
| Guilty                                 | value at prior decision point | mean within past 24 hours |
| Happy                                  | value at prior decision point | mean within past 24 hours |
| Self-regulatory capacity               | value at prior decision point | mean within past 24 hours |
| Stressor                               | value at prior decision point | sum within past 24 hours  |
| Substance use - Any substances used    | value at prior decision point | sum within past 24 hours  |
| Substance use - Any tobacco used       | value at prior decision point | sum within past 24 hours  |
| Substance use - Any marijuana used     | value at prior decision point | sum within past 24 hours  |
| Substance use - No. cigarettes smoked  | value at prior decision point | sum within past 24 hours  |
| Substance use - No. alcoholic servings | value at prior decision point | sum within past 24 hours  |

```{r}
# This is the data frame that is the output of the very last step of our data pipeline
dat_primary_aim <- readRDS(file = file.path(path_manipulated_data, "dat_primary_aim.rds")) 
dat_primary_aim <- dat_primary_aim %>%
  # Note that in contrast to H1, in H3 there is no sensitivity analysis where we re-do the analyses using all 10 days of the MRT
  mutate(is_include_main = if_else((decision_point >= 7) & (decision_point <= 54), 1, 0))                                                    
```

```{r}
dat_primary_aim <- dat_primary_aim %>%
  mutate(eligibility_lag1 = lag(eligibility)) %>%
  mutate(ashamed_lag1 = lag(ashamed), 
         guilty_lag1 = lag(guilty), 
         happy_lag1 = lag(happy),
         stressor_is_any_lag1 = lag(stressor_is_any), 
         src_scored_lag1 = lag(src_scored),
         substance_is_any_lag1 = lag(substance_is_any), 
         substance_is_any_nicotine_lag1 = lag(substance_is_any_nicotine), 
         substance_is_alcohol_lag1 = lag(substance_is_alcohol), 
         substance_is_marijuana_or_cannabis_lag1 = lag(substance_is_marijuana_or_cannabis),
         cigarette_counts_lag1 = lag(cigarette_counts), 
         alcohol_counts_lag1 = lag(alcohol_counts)) %>%
  mutate(eligibility_overall_past_dp = if_else(eligibility == 1 & eligibility_lag1 == 1, 1, 0),
         eligibility_overall_past_24h = if_else(eligibility == 1 & counts_rand_past24hrs >= 1, 1, 0))
```

```{r}
dat_primary_aim <- dat_primary_aim %>% filter(is_include_main == 1)
```

```{r}
my_list <- list(Y = -1,
                coinflip = -1,
                hour_coinflip_local = -1,
                days_between_v1_and_coinflip_local = -1,
                any_response_2qs = -1,
                any_recent_eligible_dp = -1,
                engagement_most_recent_eligible = -1,
                age = -1,
                is_female = -1,
                is_latino = -1,
                is_not_latino_and_black = -1,
                is_not_latino_and_other = -1,
                baseline_tobacco_history = -1,
                has_partner = -1,
                income_val = -1,
                # Past 1 decision point
                ashamed_lag1 = -1,
                guilty_lag1 = -1,
                happy_lag1 = -1,
                stressor_is_any_lag1 = -1,
                src_scored_lag1 = -1,
                substance_is_any_lag1 = -1,
                substance_is_any_nicotine_lag1 = -1,
                substance_is_alcohol_lag1 = -1,
                substance_is_marijuana_or_cannabis_lag1 = -1,
                cigarette_counts_lag1 = -1,
                alcohol_counts_lag1 = -1,
                # Past 24 hours
                ashamed_mean_past24hrs = -1,
                guilty_mean_past24hrs = -1,
                happy_mean_past24hrs = -1,
                src_scored_mean_past24hrs = -1,
                stressor_is_any_sum_past24hrs = -1,
                cigarette_counts_sum_past24hrs = -1,
                alcohol_counts_sum_past24hrs = -1,
                substance_is_any_sum_past24hrs = -1,
                substance_is_any_nicotine_sum_past24hrs = -1,
                substance_is_marijuana_or_cannabis_sum_past24hrs = -1,
                substance_is_alcohol_sum_past24hrs = -1)
```

# Operationalization 1

## Ashamed

```{r}
use_these_moderators <- c("ashamed_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ ashamed_lag1,  
  control_formula = ~ ashamed_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Guilty

```{r}
use_these_moderators <- c("guilty_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ guilty_lag1,  
  control_formula = ~ guilty_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```


## Happy

```{r}
use_these_moderators <- c("happy_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ happy_lag1,  
  control_formula = ~ happy_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Self-regulatory capacity

```{r}
use_these_moderators <- c("src_scored_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ src_scored_lag1,  
  control_formula = ~ src_scored_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Stressor

```{r}
use_these_moderators <- c("stressor_is_any_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ stressor_is_any_lag1,  
  control_formula = ~ stressor_is_any_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any substance use

```{r}
use_these_moderators <- c("substance_is_any_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_any_lag1,  
  control_formula = ~ substance_is_any_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any nicotine use

```{r}
use_these_moderators <- c("substance_is_any_nicotine_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_any_nicotine_lag1,  
  control_formula = ~ substance_is_any_nicotine_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- cigarette counts

```{r}
use_these_moderators <- c("cigarette_counts_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ cigarette_counts_lag1,  
  control_formula = ~ cigarette_counts_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any alcohol use

```{r}
use_these_moderators <- c("substance_is_alcohol_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_alcohol_lag1,  
  control_formula = ~ substance_is_alcohol_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- alcohol counts

```{r}
use_these_moderators <- c("alcohol_counts_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ alcohol_counts_lag1,  
  control_formula = ~ alcohol_counts_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any marijuana or cannabis

```{r}
use_these_moderators <- c("substance_is_marijuana_or_cannabis_lag1")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_dp, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_dp)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_marijuana_or_cannabis_lag1,  
  control_formula = ~ substance_is_marijuana_or_cannabis_lag1 + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```



# Operationalization 2

## Ashamed

```{r}
use_these_moderators <- c("ashamed_mean_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ ashamed_mean_past24hrs,  
  control_formula = ~ ashamed_mean_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Guilty

```{r}
use_these_moderators <- c("guilty_mean_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ guilty_mean_past24hrs,  
  control_formula = ~ guilty_mean_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Happy

```{r}
use_these_moderators <- c("happy_mean_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ happy_mean_past24hrs,  
  control_formula = ~ happy_mean_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Self-regulatory capacity

```{r}
use_these_moderators <- c("src_scored_mean_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ src_scored_mean_past24hrs,  
  control_formula = ~ src_scored_mean_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Stressor

```{r}
use_these_moderators <- c("stressor_is_any_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ stressor_is_any_sum_past24hrs,  
  control_formula = ~ stressor_is_any_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any substance use

```{r}
use_these_moderators <- c("substance_is_any_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_any_sum_past24hrs,  
  control_formula = ~ substance_is_any_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any nicotine use

```{r}
use_these_moderators <- c("substance_is_any_nicotine_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_any_nicotine_sum_past24hrs,  
  control_formula = ~ substance_is_any_nicotine_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- cigarette counts

```{r}
use_these_moderators <- c("cigarette_counts_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ cigarette_counts_sum_past24hrs,  
  control_formula = ~ cigarette_counts_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any alcohol use

```{r}
use_these_moderators <- c("substance_is_alcohol_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_alcohol_sum_past24hrs,  
  control_formula = ~ substance_is_alcohol_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- alcohol counts

```{r}
use_these_moderators <- c("alcohol_counts_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ alcohol_counts_sum_past24hrs,  
  control_formula = ~ alcohol_counts_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

## Substance use -- any marijuana or cannabis use

```{r}
use_these_moderators <- c("substance_is_marijuana_or_cannabis_sum_past24hrs")

dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, decision_point, eligibility_overall_past_24h, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val,
         all_of(use_these_moderators)) %>%
  rename(eligibility = eligibility_overall_past_24h)
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val, 
         all_of(use_these_moderators)) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ substance_is_marijuana_or_cannabis_sum_past24hrs,  
  control_formula = ~ substance_is_marijuana_or_cannabis_sum_past24hrs + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```



