---
title: "MARS MRT: H1 and Exploratory Analyses on Moderated Effect of Time"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
library(MRTAnalysis)
```
```{r}
# This is the data frame that is the output of the very last step of our data pipeline
dat_primary_aim <- readRDS(file = file.path(path_manipulated_data, "dat_primary_aim.rds")) 
```

```{r}
dat_primary_aim <- dat_primary_aim %>%
  mutate(is_include_main = if_else((decision_point >= 7) & (decision_point <= 54), 1, 0),    # Drop the first 6 and last 6 decision points
         is_include_sensitivity = 1)                                                         # Keep all decision points
```

**H1 Main Analysis** excludes first and last days of the 10-day MRT while **H1 Sensitivity Analysis** includes all days of the 10-day MRT. In **Exploratory Analysis on Moderated Effect of Time**, we investigate whether the effect of prompt (versus no prompt) varies by day in study, where day in study is modeled in a linear or quadratic manner.

# H1 Main Analysis 

```{r}
dat_for_analysis <- dat_primary_aim %>%
  filter(is_include_main == 1) %>%
  select(participant_id, decision_point, eligibility, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val)
```

```{r}
my_list <- list(Y = -1,
                coinflip = -1,
                hour_coinflip_local = -1, 
                days_between_v1_and_coinflip_local = -1,
                any_response_2qs = -1, 
                any_recent_eligible_dp = -1, 
                engagement_most_recent_eligible = -1,
                age = -1, 
                is_female = -1, 
                is_latino = -1, 
                is_not_latino_and_black = -1, 
                is_not_latino_and_other = -1, 
                baseline_tobacco_history = -1, 
                has_partner = -1, 
                income_val = -1)
```

```{r}
logical_vec_cc <- dat_for_analysis %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)

dat_summary_observed <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1) %>%
  group_by(is_complete) %>%
  summarise(total = n())

dat_summary <- data.frame(n_elig = sum(dat_summary_observed[["total"]]),
                          n_included_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == TRUE, ][["total"]],
                          n_excluded_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == FALSE, ][["total"]])

dat_summary
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```

```{r}
# Format output to 3 decimal places
summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_causal.csv"), row.names = TRUE)

summary(fit1, show_control_fit = TRUE)[["control_variables"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_control.csv"), row.names = TRUE)
```

# Exploratory Analysis (Linear Effect of Time)

```{r}
fit2 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ days_between_v1_and_coinflip_local,  
  control_formula = ~ days_between_v1_and_coinflip_local + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit2, show_control_fit = TRUE)
```

```{r}
# Format output to 3 decimal places
summary(fit2, show_control_fit = TRUE)[["causal_excursion_effect"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_causal_linear_time.csv"), row.names = TRUE)

summary(fit2, show_control_fit = TRUE)[["control_variables"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_control_linear_time.csv"), row.names = TRUE)
```

# Exploratory Analysis (Quadratic Effect of Time)

```{r}
fit3 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ days_between_v1_and_coinflip_local + I(days_between_v1_and_coinflip_local * days_between_v1_and_coinflip_local),  
  control_formula = ~ days_between_v1_and_coinflip_local + I(days_between_v1_and_coinflip_local * days_between_v1_and_coinflip_local) + age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit3, show_control_fit = TRUE)
```


```{r}
# Format output to 3 decimal places
summary(fit3, show_control_fit = TRUE)[["causal_excursion_effect"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_causal_quadratic_time.csv"), row.names = TRUE)

summary(fit3, show_control_fit = TRUE)[["control_variables"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "H1_control_quadratic_time.csv"), row.names = TRUE)
```


# H1 Sensitivity Analysis

```{r}
dat_for_analysis <- dat_primary_aim %>%
  filter(is_include_sensitivity == 1) %>%
  select(participant_id, decision_point, eligibility, 
         coinflip, Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val)
```

```{r}
my_list <- list(Y = -1,
                coinflip = -1,
                hour_coinflip_local = -1, 
                days_between_v1_and_coinflip_local = -1,
                any_response_2qs = -1, 
                any_recent_eligible_dp = -1, 
                engagement_most_recent_eligible = -1,
                age = -1, 
                is_female = -1, 
                is_latino = -1, 
                is_not_latino_and_black = -1, 
                is_not_latino_and_other = -1, 
                baseline_tobacco_history = -1, 
                has_partner = -1, 
                income_val = -1)
```

```{r}
logical_vec_cc <- dat_for_analysis %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)

dat_summary_observed <- dat_for_analysis %>% 
  mutate(is_complete = logical_vec_cc) %>% 
  filter(eligibility == 1) %>%
  group_by(is_complete) %>%
  summarise(total = n())

dat_summary <- data.frame(n_elig = sum(dat_summary_observed[["total"]]),
                          n_included_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == TRUE, ][["total"]],
                          n_excluded_among_elig = dat_summary_observed[dat_summary_observed[["is_complete"]] == FALSE, ][["total"]])

dat_summary
```

```{r}
dat_for_analysis_elig <- dat_for_analysis %>% filter(eligibility == 1)
dat_for_analysis_not_elig <- dat_for_analysis %>% filter(eligibility == 0)
```

```{r}
logical_vec_cc <- dat_for_analysis_elig %>% 
  select(Y,
         hour_coinflip_local, days_between_v1_and_coinflip_local,
         any_response_2qs, any_recent_eligible_dp, engagement_most_recent_eligible,
         age, is_female, is_latino, is_not_latino_and_black, is_not_latino_and_other, baseline_tobacco_history, has_partner, income_val) %>%
  complete.cases(.)
```

```{r}
# Note that this line is needed because we are doing a complete case analysis
# We would not need this line if we were doing a multiply imputed analysis
dat_for_analysis_elig <- dat_for_analysis_elig %>% mutate(eligibility = if_else(logical_vec_cc, eligibility, 0))
```

```{r}
dat_for_analysis <- rbind(dat_for_analysis_elig, dat_for_analysis_not_elig)
dat_for_analysis <- dat_for_analysis %>% arrange(participant_id, decision_point)
dat_for_analysis <- dat_for_analysis %>% replace_na(my_list)
```

```{r}
fit1 <- emee(
  data = dat_for_analysis,
  id = "participant_id",  
  outcome = "Y",
  treatment = "coinflip",
  rand_prob = 0.5,
  moderator_formula = ~ 1,  
  control_formula = ~ age + is_female + is_latino + is_not_latino_and_black + is_not_latino_and_other + baseline_tobacco_history + has_partner + income_val + hour_coinflip_local + days_between_v1_and_coinflip_local + any_response_2qs + any_recent_eligible_dp + engagement_most_recent_eligible, 
  availability = "eligibility"
)

summary(fit1, show_control_fit = TRUE)
```


```{r}
# Format output to 3 decimal places
summary(fit1, show_control_fit = TRUE)[["causal_excursion_effect"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "sensitivity_H1_causal.csv"), row.names = TRUE)

summary(fit1, show_control_fit = TRUE)[["control_variables"]] %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "sensitivity_H1_control.csv"), row.names = TRUE)
```




