---
title: "MARS MRT: Day-Level Analyses"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>
```
```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
library(geepack)
library(tvem)
```

```{r}
is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output"))
}

is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use"))
}
```

```{r}
# This is the data frame that is the output of the very last step of our data pipeline
dat_primary_aim <- readRDS(file = file.path(path_manipulated_data, "dat_primary_aim.rds"))
```

```{r}
these_control_covariates <- c("age", "is_male", "is_latino", "is_not_latino_and_black", "is_not_latino_and_other", "baseline_tobacco_history", "has_partner", "income_val", "hour_coinflip_local", "days_between_v1_and_coinflip_local", "any_response_2qs", "any_recent_eligible_dp", "engagement_most_recent_eligible")
```

```{r}
dat_baseline <- dat_primary_aim %>% filter(decision_point == 1) %>% select(participant_id, all_of(these_control_covariates))
```

```{r}
dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, cluster_id, decision_point,
         Y, cigarette_counts, eligibility, coinflip, is_high_effort, is_low_effort) %>%
  mutate(coinflip = replace(coinflip, eligibility == 0, 0)) %>%
  group_by(participant_id, cluster_id) %>%
  summarise(n_elig = sum(eligibility),
            n_any_prompt = sum(coinflip),
            n_obs_engaged = sum(!is.na(Y)),
            n_obs_nic = sum(!is.na(cigarette_counts)),
            n_engaged = sum(Y, na.rm = TRUE),
            n_nic = sum(cigarette_counts, na.rm = TRUE)) %>%
  ungroup(.)
```

```{r}
dat_for_analysis <- dat_for_analysis %>%
  mutate(n_nic_lag1 = lag(n_nic),
         n_elig_lag1 = lag(n_elig),
         n_obs_nic_lag1 = lag(n_obs_nic),
         n_engaged_lag1 = lag(n_engaged)) %>%
  mutate(n_any_prompt_lag1 = lag(n_any_prompt)) %>%
  mutate(n_obs_nic_lead1 = lead(n_obs_nic),
         n_nic_lead1 = lead(n_nic),
         n_elig_lead1 = lead(n_elig)) %>%
  mutate(any_nic = 1*(n_nic > 0),
         any_nic_lag1 = 1*(n_nic_lag1 > 0),
         any_nic_lead1 = 1*(n_nic_lead1 > 0)) %>%
  mutate(any_engaged = 1*(n_engaged > 0),
         any_engaged_lag1 = 1*(n_engaged_lag1 > 0)) %>%
  filter(cluster_id >= 2 & cluster_id <= 9)

dat_for_analysis <- dat_for_analysis %>% mutate(cluster_id = cluster_id - 1) # So that day in MRT will begin at 0 rather than 1
```

```{r}
dat_for_analysis <- left_join(x = dat_for_analysis, y = dat_baseline, by = join_by(participant_id == participant_id))
```

# Association between engagement in self-regulatory strategies and cigarette use on current day

$$
\mathrm{logit} Pr \left( \text{ANY CIGARETTE USE}_{i,d} = 1 \Bigg| \sum_{b = 1}^6 I_{i, d, b} \geq 1, \text{control covariates}, \text{NO. OF TIMES ENGAGED}_{i,d} \right) = \beta_0 + \text{c_age}\beta_1 + \text{c_is_male}\beta_2 + \text{c_is_latino}\beta_3 + \text{c_is_not_latino_and_black}\beta_4 + \text{c_is_not_latino_and_other}\beta_5 + \text{c_baseline_tobacco_history}\beta_6 + \text{c_has_partner}\beta_7 + \text{c_income_val}\beta_8 + \text{c_any_prompt_counts}_{i,d}\beta_9 + \text{NO. TIMES ENGAGED}_{i,d} \beta_{10}
$$

```{r}
dat_logreg <- dat_for_analysis %>% 
  filter(n_elig > 0) %>%
  filter(n_elig == n_obs_nic) %>%
  select(participant_id, cluster_id, 
         n_elig, n_obs_nic, n_any_prompt,
         n_nic, any_nic, n_engaged,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val) %>%
  mutate(drop_row = if_else(!complete.cases(.), 1, 0)) %>%
  filter(drop_row == 0)
```

```{r}
dat_tmp <- dat_logreg %>% 
  select(participant_id,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val) %>%
  unique(.)
```

```{r}
dat_tmp_summary <- dat_tmp %>%
  summarise(m_age = mean(age),
            m_is_male = mean(is_male),
            m_is_latino = mean(is_latino),
            m_is_not_latino_and_black = mean(is_not_latino_and_black),
            m_is_not_latino_and_other = mean(is_not_latino_and_other),
            m_baseline_tobacco_history = mean(baseline_tobacco_history),
            m_has_partner = mean(has_partner),
            m_income_val = mean(income_val))
```

```{r}
dat_logreg <- cbind(dat_logreg, dat_tmp_summary)
```

```{r}
dat_tmp2 <- dat_logreg %>% select(participant_id, cluster_id, n_any_prompt)
```

```{r}
dat_tmp2_summary <- dat_tmp2 %>%
  group_by(cluster_id) %>%
  summarise(m_any_prompt_counts = mean(n_any_prompt))
```

```{r}
dat_logreg <- left_join(x = dat_logreg, y = dat_tmp2_summary, by = join_by(cluster_id == cluster_id))
```

```{r}
dat_logreg <- dat_logreg %>%
  mutate(c_age = age - m_age,
         c_is_male = is_male - m_is_male, 
         c_is_latino = is_latino - m_is_latino, 
         c_is_not_latino_and_black = is_not_latino_and_black - m_is_not_latino_and_black, 
         c_is_not_latino_and_other = is_not_latino_and_other - m_is_not_latino_and_other, 
         c_baseline_tobacco_history = baseline_tobacco_history - m_baseline_tobacco_history, 
         c_has_partner = has_partner - m_has_partner, 
         c_income_val = income_val - m_income_val) %>%
  mutate(c_any_prompt_counts = n_any_prompt - m_any_prompt_counts)
```

```{r}
fit <- geeglm(any_nic ~ c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts + n_engaged, 
              family = "binomial", 
              data = dat_logreg, 
              id = participant_id, 
              waves = cluster_id)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]

dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results[["LB90"]] <- dat_results$Estimate - qnorm(0.95) * dat_results$Std.err
dat_results[["UB90"]] <- dat_results$Estimate + qnorm(0.95) * dat_results$Std.err


dat_results_logodds_scale <- dat_results
dat_results_logodds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_logodds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_log_odds_scale_concurrent.csv"), row.names = TRUE)
```

```{r}
dat_results_odds_scale <- data.frame(estimate = exp(dat_results$Estimate), 
                                     # 95% CI
                                     LB95 = exp(dat_results[["LB95"]]), 
                                     UB95 = exp(dat_results[["UB95"]]),
                                     # 90% CI
                                     LB90 = exp(dat_results[["LB90"]]), 
                                     UB90 = exp(dat_results[["UB90"]]))

row.names(dat_results_odds_scale) <- row.names(dat_results_logodds_scale)

dat_results_odds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_odds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_odds_scale_concurrent.csv"), row.names = TRUE)
```

$$
E \left( \text{NO. CIGARETTES SMOKED}_{i,d} \Bigg| \sum_{b = 1}^6 I_{i, d, b} \geq 1, \text{control covariates}, \text{NO. OF TIMES ENGAGED}_{i,d} \right) = \beta_0 + \text{c_age}\beta_1 + \text{c_is_male}\beta_2 + \text{c_is_latino}\beta_3 + \text{c_is_not_latino_and_black}\beta_4 + \text{c_is_not_latino_and_other}\beta_5 + \text{c_baseline_tobacco_history}\beta_6 + \text{c_has_partner}\beta_7 + \text{c_income_val}\beta_8 + \text{c_any_prompt_counts}_{i,d}\beta_9 + \text{NO. TIMES ENGAGED}_{i,d} \beta_{10}
$$


```{r}
fit <- geeglm(n_nic ~ c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts + n_engaged, 
              data = dat_logreg, 
              id = participant_id, 
              waves = cluster_id)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]

dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results[["LB90"]] <- dat_results$Estimate - qnorm(0.95) * dat_results$Std.err
dat_results[["UB90"]] <- dat_results$Estimate + qnorm(0.95) * dat_results$Std.err


dat_results_mean_scale <- dat_results
dat_results_mean_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_mean_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_mean_scale_concurrent.csv"), row.names = TRUE)
```

```{r}
mu <- mean(dat_logreg$n_engaged)
std_dev <- sd(dat_logreg$n_engaged)
mu_plus_1sd <- mu + std_dev
mu_minus_1sd <- mu - std_dev

data.frame(mu = mu, std_dev = std_dev)

est_beta <- as.matrix(dat_results$Estimate)
Lmat <- rbind(c(1, rep(0,9), mu),
              c(1, rep(0,9), mu_plus_1sd),
              c(1, rep(0,9), mu_minus_1sd))
Vmat <- vcov(fit)

est_rate <- Lmat %*% est_beta
std_err_rate <- sqrt(diag(Lmat %*% Vmat %*% t(Lmat)))

LB95_rate <- est_rate - qnorm(0.975)*std_err_rate
UB95_rate <- est_rate + qnorm(0.975)*std_err_rate

LB90_rate <- est_rate - qnorm(0.95)*std_err_rate
UB90_rate <- est_rate + qnorm(0.95)*std_err_rate

dat_results_rate <- data.frame(estimate = est_rate,
                               # 95% CI
                               LB95 = LB95_rate, 
                               UB95 = UB95_rate,
                               # 90% CI
                               LB90 = LB90_rate, 
                               UB90 = UB90_rate)

row.names(dat_results_rate) <- c("rate at the mean of control covariates when mu", "rate at the mean of control covariates when mu+1*sd", "rate at the mean of control covariates when mu-1*sd")

dat_results_rate  %>% round(., 3)

# Format output to 3 decimal places
dat_results_rate %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_rate_concurrent.csv"), row.names = TRUE)
```

# Time-varying association between engagement in self-regulatory strategies and cigarette use on current day

$$
\text{logit} Pr\left(\text{ANY CIGARETTE USE}_{i} \left(t_{i,d} \right) = 1\right) = \boldsymbol{Z}_c\boldsymbol{\alpha} + \beta_0 \left(t_{i,d}\right) + \text{c_any_prompt_counts}\left(t_{i,d}\right) \beta_1 \left(t_{i,d}\right)  + \text{NO. OF TIMES ENGAGED} \left(t_{i,d}\right) \beta_2 \left(t_{i,d}\right) 
$$

where $\boldsymbol{Z}_c$ denotes centered baseline covariates.

```{r}
dat_tvem <- dat_logreg
```

```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=any_nic ~ c_any_prompt_counts + n_engaged,
                     id=participant_id,
                     time=cluster_id,
                     invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                     family = binomial(),
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=any_nic ~ c_any_prompt_counts + n_engaged,
                   id=participant_id,
                   time=cluster_id,
                   invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                   family = binomial(),
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)
```

```{r}
plot(model_tvem)

plot(model_tvem, exponentiate = TRUE)
```

```{r}
# Create ggplot version of plot
dat_fitted_tvem <- model_tvem$grid_fitted_coefficients$n_engaged

dat_fitted_tvem[["time_grid"]] <- model_tvem$time_grid

dat_fitted_tvem[["UB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error

dat_fitted_tvem[["UB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_logodds_scale_concurrent_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_logodds_scale_concurrent_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```


```{r}
# Create ggplot version of plot
dat_fitted_tvem_exp_scale <- dat_fitted_tvem

dat_fitted_tvem_exp_scale[["estimate"]] <- exp(dat_fitted_tvem[["estimate"]])

dat_fitted_tvem_exp_scale[["UB95"]] <- exp(dat_fitted_tvem[["UB95"]])
dat_fitted_tvem_exp_scale[["LB95"]] <- exp(dat_fitted_tvem[["LB95"]])

dat_fitted_tvem_exp_scale[["UB90"]] <- exp(dat_fitted_tvem[["UB90"]])
dat_fitted_tvem_exp_scale[["LB90"]] <- exp(dat_fitted_tvem[["LB90"]])
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem_exp_scale, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.3, linetype = 2, linewidth = 2, color = "black", fill = "thistle3") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 1, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(0, 2))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_odds_scale_concurrent_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem_exp_scale, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.3, linetype = 2, linewidth = 2, color = "black", fill = "thistle3") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 1, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(0, 2))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_odds_scale_concurrent_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

$$
E\left(\text{NO. OF CIGARETTES SMOKED}_{i} \left(t_{i,j} \right) = 1\right) = \boldsymbol{Z}_c\boldsymbol{\alpha} + \beta_0 \left(t_{i,d}\right) + \text{c_any_prompt_counts}\left(t_{i,d}\right) \beta_1 \left(t_{i,d}\right)  + \text{NO. OF TIMES ENGAGED} \left(t_{i,d}\right) \beta_2 \left(t_{i,d}\right)
$$

where $\boldsymbol{Z}_c$ denotes centered baseline covariates.


```{r}
dat_tvem <- dat_logreg
```

```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=n_nic ~ c_any_prompt_counts + n_engaged,
                     id=participant_id,
                     time=cluster_id,
                     invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=n_nic ~  c_any_prompt_counts + n_engaged,
                   id=participant_id,
                   time=cluster_id,
                   invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)
```

```{r}
plot(model_tvem)
```

```{r}
# Create ggplot version of plot
dat_fitted_tvem <- model_tvem$grid_fitted_coefficients$n_engaged

dat_fitted_tvem[["time_grid"]] <- model_tvem$time_grid

dat_fitted_tvem[["UB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error

dat_fitted_tvem[["UB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_mean_scale_concurrent_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_mean_scale_concurrent_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```


# Association between engagement in self-regulatory strategies and cigarette use on next day

$$
\mathrm{logit} Pr \left( \text{ANY CIGARETTE USE}_{i,d + 1} = 1 \Bigg| \left\{\sum_{b = 1}^6 I_{i,d, b} \geq 1\right\} \cap \left\{\sum_{b = 1}^6 I_{i,d+1, b} \geq 1\right\} , \text{control covariates}, \text{NO. OF TIMES ENGAGED}_{i,d} \right) = \beta_0 + \text{c_age}\beta_1 + \text{c_is_male}\beta_2 + \text{c_is_latino}\beta_3 + \text{c_is_not_latino_and_black}\beta_4 + \text{c_is_not_latino_and_other}\beta_5 + \text{c_baseline_tobacco_history}\beta_6 + \text{c_has_partner}\beta_7 + \text{c_income_val}\beta_8 + \text{c_any_prompt_counts}_{i,d}\beta_9 + \text{ANY CIGARETTE USE}_{i,d}\beta_{10} + \text{NO. TIMES ENGAGED}_{i,d} \beta_{11}
$$

```{r}
dat_logreg <- dat_for_analysis %>% 
  filter((n_elig > 0) & (n_elig_lead1 > 0)) %>%
  filter((n_elig == n_obs_nic) & (n_elig_lead1 == n_obs_nic_lead1)) %>%
  select(participant_id, cluster_id, 
         n_elig, n_obs_nic, n_any_prompt,
         n_elig_lead1, n_obs_nic_lead1,
         n_nic, any_nic, n_engaged,
         n_nic_lead1, any_nic_lead1,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val) %>%
  mutate(drop_row = if_else(!complete.cases(.), 1, 0)) %>%
  filter(drop_row == 0)
```

```{r}
dat_tmp <- dat_logreg %>% 
  select(participant_id,
         age, is_male, is_latino, is_not_latino_and_black, is_not_latino_and_other, 
         baseline_tobacco_history, has_partner, income_val) %>%
  unique(.)
```

```{r}
dat_tmp_summary <- dat_tmp %>%
  summarise(m_age = mean(age),
            m_is_male = mean(is_male),
            m_is_latino = mean(is_latino),
            m_is_not_latino_and_black = mean(is_not_latino_and_black),
            m_is_not_latino_and_other = mean(is_not_latino_and_other),
            m_baseline_tobacco_history = mean(baseline_tobacco_history),
            m_has_partner = mean(has_partner),
            m_income_val = mean(income_val))
```

```{r}
dat_logreg <- cbind(dat_logreg, dat_tmp_summary)
```

```{r}
dat_tmp2 <- dat_logreg %>% select(participant_id, cluster_id, n_any_prompt, any_nic, n_nic)
```

```{r}
dat_tmp2_summary <- dat_tmp2 %>%
  group_by(cluster_id) %>%
  summarise(m_any_prompt_counts = mean(n_any_prompt),
            m_any_nic = mean(any_nic),
            m_n_nic = mean(n_nic))
```

```{r}
dat_logreg <- left_join(x = dat_logreg, y = dat_tmp2_summary, by = join_by(cluster_id == cluster_id))
```

```{r}
dat_logreg <- dat_logreg %>%
  mutate(c_age = age - m_age,
         c_is_male = is_male - m_is_male, 
         c_is_latino = is_latino - m_is_latino, 
         c_is_not_latino_and_black = is_not_latino_and_black - m_is_not_latino_and_black, 
         c_is_not_latino_and_other = is_not_latino_and_other - m_is_not_latino_and_other, 
         c_baseline_tobacco_history = baseline_tobacco_history - m_baseline_tobacco_history, 
         c_has_partner = has_partner - m_has_partner, 
         c_income_val = income_val - m_income_val) %>%
  mutate(c_any_prompt_counts = n_any_prompt - m_any_prompt_counts,
         c_any_nic = any_nic - m_any_nic,
         c_n_nic = n_nic - m_n_nic)
```

```{r}
fit <- geeglm(any_nic_lead1 ~ c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts + c_any_nic + n_engaged, family = "binomial", data = dat_logreg, id = participant_id, waves = cluster_id)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]

dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results[["LB90"]] <- dat_results$Estimate - qnorm(0.95) * dat_results$Std.err
dat_results[["UB90"]] <- dat_results$Estimate + qnorm(0.95) * dat_results$Std.err

dat_results_logodds_scale <- dat_results
dat_results_logodds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_logodds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_log_odds_scale_lagged.csv"), row.names = TRUE)
```

```{r}
dat_results_odds_scale <- data.frame(estimate = exp(dat_results$Estimate), 
                                     # 95% CI
                                     LB95 = exp(dat_results[["LB95"]]), 
                                     UB95 = exp(dat_results[["UB95"]]),
                                     # 90% CI
                                     LB90 = exp(dat_results[["LB90"]]), 
                                     UB90 = exp(dat_results[["UB90"]]))

row.names(dat_results_odds_scale) <- row.names(dat_results_logodds_scale)

dat_results_odds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_odds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_odds_scale_lagged.csv"), row.names = TRUE)
```

$$
E \left( \text{NO. CIGARETTES SMOKED}_{i,d+1} \Bigg| \sum_{b = 1}^6 I_{i, d, b} \geq 1, \text{control covariates}, \text{NO. OF TIMES ENGAGED}_{i,d} \right) = \beta_0 + \text{c_age}\beta_1 + \text{c_is_male}\beta_2 + \text{c_is_latino}\beta_3 + \text{c_is_not_latino_and_black}\beta_4 + \text{c_is_not_latino_and_other}\beta_5 + \text{c_baseline_tobacco_history}\beta_6 + \text{c_has_partner}\beta_7 + \text{c_income_val}\beta_8 + \text{c_any_prompt_counts}_{i,d}\beta_9 + \text{c_NO. CIGARETTES SMOKED}\beta_{10} + \text{NO. TIMES ENGAGED}_{i,d} \beta_{11}
$$

```{r}
fit <- geeglm(n_nic_lead1 ~ c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts + c_n_nic + n_engaged, data = dat_logreg, id = participant_id, waves = cluster_id)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]

dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results[["LB90"]] <- dat_results$Estimate - qnorm(0.95) * dat_results$Std.err
dat_results[["UB90"]] <- dat_results$Estimate + qnorm(0.95) * dat_results$Std.err

dat_results_mean_scale <- dat_results
dat_results_mean_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_mean_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "day_level_mean_scale_lagged.csv"), row.names = TRUE)
```

# Time-varying association between engagement in self-regulatory strategies and next day cigarette use

```{r}
dat_tvem <- dat_logreg
```

$$
\text{logit} Pr\left(\text{ANY CIGARETTE USE}_{i} \left(t_{i,d+1} \right) = 1\right)= \boldsymbol{Z}_c\boldsymbol{\alpha} + \beta_0 \left(t_{i,d}\right) + \beta_1 \left(t_{i,d}\right) \text{c_ANY PROMPT}_{i} \left(t_{i,d} \right) + \beta_2 \left(t_{i,d}\right) \text{c_ANY CIGARETTE USE}_{i} \left(t_{i,d} \right) + \beta_3 \left(t_{i,d}\right) \text{WHETHER ENGAGED} \left(t_{i,d}\right)
$$

where $\boldsymbol{Z}_c$ denotes centered baseline covariates.


```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=any_nic_lead1 ~ c_any_nic + n_engaged,
                     id=participant_id,
                     time=cluster_id,
                     invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts,
                     family = binomial(),
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=any_nic_lead1 ~ c_any_nic + n_engaged,
                   id=participant_id,
                   time=cluster_id,
                   invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val + c_any_prompt_counts,
                   family = binomial(),
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)
```

```{r}
plot(model_tvem)

plot(model_tvem, exponentiate = TRUE)
```

```{r}
# Create ggplot version of plot
dat_fitted_tvem <- model_tvem$grid_fitted_coefficients$n_engaged

dat_fitted_tvem[["time_grid"]] <- model_tvem$time_grid

dat_fitted_tvem[["UB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error

dat_fitted_tvem[["UB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_logodds_scale_lagged_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_logodds_scale_lagged_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```


```{r}
# Create ggplot version of plot
dat_fitted_tvem_exp_scale <- dat_fitted_tvem

dat_fitted_tvem_exp_scale[["estimate"]] <- exp(dat_fitted_tvem[["estimate"]])

dat_fitted_tvem_exp_scale[["UB95"]] <- exp(dat_fitted_tvem[["UB95"]])
dat_fitted_tvem_exp_scale[["LB95"]] <- exp(dat_fitted_tvem[["LB95"]])

dat_fitted_tvem_exp_scale[["UB90"]] <- exp(dat_fitted_tvem[["UB90"]])
dat_fitted_tvem_exp_scale[["LB90"]] <- exp(dat_fitted_tvem[["LB90"]])
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem_exp_scale, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.3, linetype = 2, linewidth = 2, color = "black", fill = "thistle3") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 1, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(0, 2))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_odds_scale_lagged_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem_exp_scale, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.3, linetype = 2, linewidth = 2, color = "black", fill = "thistle3") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 1, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(0, 2))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_odds_scale_lagged_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
dat_tvem <- dat_logreg
```

$$
E\left(\text{NO. OF CIGARETTES SMOKED}_{i} \left(t_{i,j+1} \right) = 1\right) = = 1\right)= \boldsymbol{Z}_c\boldsymbol{\alpha} + \beta_0 \left(t_{i,d}\right) + \beta_1 \left(t_{i,d}\right) \text{c_ANY PROMPT}_{i} \left(t_{i,d} \right) + \beta_2 \left(t_{i,d}\right) \text{c_NO. OF CIGARETTES SMOKED}_{i} \left(t_{i,d} \right) + \beta_3 \left(t_{i,d}\right) \text{WHETHER ENGAGED} \left(t_{i,d}\right)
$$
where $\boldsymbol{Z}_c$ denotes centered baseline covariates.

```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=n_nic_lead1 ~ c_any_prompt_counts + c_n_nic + n_engaged,
                     id=participant_id,
                     time=cluster_id,
                     invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=any_nic_lead1 ~ c_any_prompt_counts + c_n_nic + n_engaged,
                   id=participant_id,
                   time=cluster_id,
                   invar_effects=~c_age + c_is_male + c_is_latino + c_is_not_latino_and_black + c_is_not_latino_and_other + c_baseline_tobacco_history + c_has_partner + c_income_val,
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)
```

```{r}
plot(model_tvem)
```

```{r}
# Create ggplot version of plot
dat_fitted_tvem <- model_tvem$grid_fitted_coefficients$n_engaged

dat_fitted_tvem[["time_grid"]] <- model_tvem$time_grid

dat_fitted_tvem[["UB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB95"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.975)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error

dat_fitted_tvem[["UB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate + qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
dat_fitted_tvem[["LB90"]] <- model_tvem$grid_fitted_coefficients$n_engaged$estimate - qnorm(0.95)*model_tvem$grid_fitted_coefficients$n_engaged$standard_error
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB95, ymax = UB95), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_mean_scale_lagged_CI95.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
# Create ggplot version of plot
ggplot(dat_fitted_tvem, aes(time_grid, estimate)) + geom_line(linewidth = 2) + geom_ribbon(aes(ymin = LB90, ymax = UB90), alpha = 0.2, linetype = 2, linewidth = 2, color = "black", fill = "aquamarine4") + scale_x_continuous(limits = c(1,8), breaks = seq(1,8,1)) + xlab("Day in MRT d") + ylab("") + geom_hline(yintercept = 0, color = "red", linewidth = 2, linetype = "dotted") + ggtitle("") + scale_y_continuous(limits = c(-1.5, 1))

ggsave(filename = file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "tvem_day_level_mean_scale_lagged_CI90.png"), dpi = 1000, units = "in", height = 7, width = 12)
```

```{r}
if(file.exists("analysis-complete-case/formatted-output/Exploratory-Analysis-Associational-Cigarette-Use/Thumbs.db")){
  file.remove("analysis-complete-case/formatted-output/Exploratory-Analysis-Associational-Cigarette-Use/Thumbs.db")
}
```

