---
title: "MARS MRT: Block-Level Analyses"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: TRUE
---

```{=html}
<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
library(knitr)
library(tidyverse)
library(geepack)
library(tvem)
```

```{r}
is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output"))
}

is_dir_exist <- file.exists(file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use"))

if(isFALSE(is_dir_exist)){
  dir.create(file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use"))
}
```

```{r}
expit <- function(x){
  return(exp(x)/(1 + exp(x)))
}
```

```{r}
dat_primary_aim <- readRDS(file = file.path(path_manipulated_data, "dat_primary_aim.rds"))
```

```{r}
dat_for_analysis <- dat_primary_aim %>%
  select(participant_id, cluster_id, decision_point,
         Y, substance_is_cigarettes, eligibility, coinflip, is_high_effort, is_low_effort) %>% 
  mutate(coinflip = replace(coinflip, eligibility == 0, 0),
         is_high_effort = replace(is_high_effort, eligibility == 0, 0)) %>% 
  group_by(participant_id) %>% 
  mutate(substance_is_cigarettes_lead1 = lead(substance_is_cigarettes),
         eligibility_lead1 = lead(eligibility)) %>%
  ungroup(.) %>%
  filter((decision_point >= 7) & (decision_point <= 54))
```


# Marginal association between engagement in self-regulatory strategies and cigarette use on current person-block

$$
\mathrm{logit} Pr \left( S_{i,j} = 1 \Big| I_{i, j} = 1 \right) = \beta_0 + \beta_1 X_{i,j}
$$

```{r}
dat_logreg <- dat_for_analysis %>% 
  filter(eligibility == 1) %>% 
  select(participant_id, decision_point, substance_is_cigarettes, Y) %>%
  mutate(drop_row = if_else(!complete.cases(.), 1, 0)) %>%
  filter(drop_row == 0)
```

```{r}
fit <- geeglm(substance_is_cigarettes ~ Y, family = "binomial", data = dat_logreg, id = participant_id, waves = decision_point)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]
dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results_logodds_scale <- dat_results
dat_results_logodds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_logodds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "block_level_log_odds_scale_concurrent.csv"), row.names = TRUE)
```

```{r}
dat_results_odds_scale <- data.frame(estimate = expit(dat_results$Estimate), LB95 = expit(dat_results[["LB95"]]), UB95 = expit(dat_results[["UB95"]]))
dat_results_odds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_odds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "block_level_odds_scale_concurrent.csv"), row.names = TRUE)
```

# Estimate the prevalence

```{r}
dat_logreg <- dat_for_analysis %>% 
  filter(eligibility == 1) %>% 
  select(participant_id, decision_point, substance_is_cigarettes, Y) %>%
  mutate(drop_row = if_else(!complete.cases(.), 1, 0)) %>%
  filter(drop_row == 0)
```

```{r}
fit <- geeglm(substance_is_cigarettes ~ Y, family = "binomial", data = dat_logreg, id = participant_id, waves = decision_point)
```

```{r}
Lmat <- matrix(c(1,0,
                 1,1), ncol = 2, byrow = TRUE)

est_contrast <- Lmat %*% as.matrix(fit$coefficients)
est_vcov_contrast <- Lmat %*% vcov(fit) %*% t(Lmat)
est_stderr_contrast <- sqrt(diag(est_vcov_contrast))
LB95 <- est_contrast - qnorm(0.975) * est_stderr_contrast
UB95 <- est_contrast + qnorm(0.975) * est_stderr_contrast

expit <- function(x){
  exp(x)/(1 + exp(x))
}

dat_result <- data.frame(engaged = c(0,1), est_contrast = expit(est_contrast), LB95 = expit(LB95), UB95 = expit(UB95))
```

```{r}
print(dat_result)
```

```{r, fig.height = 5, fig.width = 7}
plot(dat_result$engaged, dat_result$est_contrast, type = "b", yaxt = "n", xaxt = "n", ylim = c(0,1), xlab = "Whether engaged in self-regulatory strategies on block j", ylab = "Prevalance of cigarette use on block j")
axis(1, at = c(0,1))
axis(2, at = seq(0,1,0.2))
lines(dat_result$engaged, dat_result$LB, type = "b", lty = 2)
lines(dat_result$engaged, dat_result$UB, type = "b", lty = 2)
```


# Time-varying association between engagement in self-regulatory strategies and cigarette use on current person-block

$$
\text{logit} Pr\left(\text{ANY CIGARETTE USE}_{i} \left(t_{i,j} \right) = 1\right)= \beta_0 \left(t_{i,j}\right) + \beta_1 \left(t_{i,j}\right) \text{WHETHER ENGAGED} \left(t_{i,j}\right)
$$
```{r}
dat_tvem <- dat_logreg
```

```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=substance_is_cigarettes ~ Y,
                     id=participant_id,
                     time=decision_point,
                     invar_effects=NULL,
                     family = binomial(),
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=substance_is_cigarettes ~ Y,
                   id=participant_id,
                   time=decision_point,
                   invar_effects=NULL,
                   family = binomial(),
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)

plot(model_tvem)
```

# Marginal association between engagement in self-regulatory strategies and cigarette use on next person-block

$$
\mathrm{logit} Pr \left( S_{i,j + 1} = 1 \Big| \left\{I_{i, j} = 1\right\} \cap \left\{I_{i, j+1} = 1\right\} \right) = \beta_0 + \beta_1 \text{WHETHER ENGAGED}_{i,j} + \beta_2 S_{i, j}
$$

```{r}
dat_logreg <- dat_for_analysis %>% 
  filter((eligibility == 1) & (eligibility_lead1 == 1)) %>% 
  select(participant_id, decision_point, substance_is_cigarettes_lead1, substance_is_cigarettes, Y) %>%
  mutate(drop_row = if_else(!complete.cases(.), 1, 0)) %>%
  filter(drop_row == 0)
```

```{r}
fit <- geeglm(substance_is_cigarettes_lead1 ~ Y + substance_is_cigarettes, family = "binomial", data = dat_logreg, id = participant_id, waves = decision_point)
```

```{r}
dat_results <- summary(fit)[["coefficients"]]
dat_results[["LB95"]] <- dat_results$Estimate - qnorm(0.975) * dat_results$Std.err
dat_results[["UB95"]] <- dat_results$Estimate + qnorm(0.975) * dat_results$Std.err

dat_results_logodds_scale <- dat_results
dat_results_logodds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_logodds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "block_level_log_odds_scale_lagged.csv"), row.names = TRUE)
```

```{r}
dat_results_odds_scale <- data.frame(estimate = expit(dat_results$Estimate), LB95 = expit(dat_results[["LB95"]]), UB95 = expit(dat_results[["UB95"]]))
dat_results_odds_scale %>% round(., 3)

# Format output to 3 decimal places
dat_results_odds_scale %>% round(., 3) %>% format(., nsmall = 3) %>% write.csv(., file.path("analysis-complete-case", "formatted-output", "Exploratory-Analysis-Associational-Cigarette-Use", "block_level_odds_scale_lagged.csv"), row.names = TRUE)
```

# Time-varying association between engagement in self-regulatory strategies and cigarette use on current person-block

$$
\text{logit} Pr\left(\text{ANY CIGARETTE USE}_{i} \left(t_{i,j+1} \right) = 1\right)= \beta_0 \left(t_{i,j}\right) + \beta_1 \left(t_{i,j}\right) \text{WHETHER ENGAGED} \left(t_{i,j}\right) + \text{ANY CIGARETTE USE}_{i} \left(t_{i,j} \right)
$$
```{r}
dat_tvem <- dat_logreg
```

```{r}
list_collect_metrics <- list()

for(current_num_knots in 1:3){
  model_tvem <- tvem(data=dat_tvem,
                     formula=substance_is_cigarettes_lead1 ~ Y + substance_is_cigarettes,
                     id=participant_id,
                     time=decision_point,
                     invar_effects=NULL,
                     family = binomial(),
                     num_knots = current_num_knots,
                     spline_order = 3,
                     penalty_function_order = 1,
                     penalize = TRUE)
  
  dat_current_metrics <- data.frame(total_knots = current_num_knots,
                                    penalty = 1,
                                    aic_value = model_tvem$model_information$pseudo_aic,
                                    bic_value = model_tvem$model_information$pseudo_bic)
  list_collect_metrics <- append(list_collect_metrics, list(dat_current_metrics))
}

dat_all_metrics <- bind_rows(list_collect_metrics)

model_tvem <- tvem(data=dat_tvem,
                   formula=substance_is_cigarettes_lead1 ~ Y + substance_is_cigarettes,
                   id=participant_id,
                   time=decision_point,
                   invar_effects=NULL,
                   family = binomial(),
                   num_knots = dat_all_metrics[which.min(dat_all_metrics$bic_value),"total_knots"],
                   spline_order = 3,
                   penalty_function_order = 1,
                   penalize = TRUE)

plot(model_tvem)
```
