---
title: "CONSORT: Tracking Data Exclusion"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    number_sections: FALSE
---

<style type="text/css">
.main-container {
  max-width: 1800px !important;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(width = 7000)
```

```{r}
source("paths.R")
source("prepare-analytic-datasets/functions-for-analytical-dataset-creation.R")
library(tidyverse)
```

```{r}
# This dataset was the output of the matching procedure
dat_all_burst <- readRDS(file = file.path(path_manipulated_data, "dat_all_burst.rds"))
# These were the sequences we have identified to be inconsistent with study protocol
# We also note the decisions on how we handled each case in this file
dat_decisions_atypical_sequences <- readRDS(file = file.path(path_manipulated_data, "dat_decisions_atypical_sequences.rds"))
# This is the dataset that results from applying the decisions to handle sequences we have found to be inconsistent with study protocol
# This dataset also includes an indicator as to whether we regarded a sequence as being outside of a participant's designated 10-day MRT period
dat_cleaned_burst_with_outside_study_indicator <- readRDS(file = file.path(path_manipulated_data, "dat_cleaned_burst_with_outside_study_indicator.rds"))
# These are the participants that we will excluded from all analyses
mars_ids_excluded_from_all_analytic_datasets <- readRDS(file = file.path(path_manipulated_data, "mars_ids_excluded_from_all_analytic_datasets.rds"))
mars_ids_pilot <- readRDS(file = file.path(path_manipulated_data, "mars_ids_pilot.rds"))
mars_ids_did_not_meet_ema_completion_criteria <- readRDS(file = file.path(path_manipulated_data, "mars_ids_did_not_meet_ema_completion_criteria.rds"))
# This dataset contains data from only those sequences which began
# within the 10-day MRT period.
dat_matched_to_decision_points <- readRDS(file = file.path(path_manipulated_data, "dat_matched_to_decision_points.rds"))
```

Our approach to deriving the analytic dataset has three phases:

* Phase 1: Applying a matching procedure (data linkage algorithm)
* Phase 2: Applying decisions common to all analyses
* Phase 3: Define outcome analysis population for each hypothesis

This document covers documentation on quantifying data excluded in Phase 1 and Phase 2.

# Phase 1

```{r}
n_participants <- length(unique(dat_all_burst[["mars_id"]]))
n_rand <- sum(!is.na(dat_all_burst[["ts_coinflip_mountain"]]))
```

* Number of participants at the start of Phase 1: `r n_participants`
* Number of micro-randomizations at the start of Phase 1: `r n_rand`

```{r}
# Note that sequences that are inconsistent with study protocol appear as 
# two rows in dat_all_burst. Therefore to get the correct number of sequences 
# obtained after the matching process we have to subtract off the number of 
# inconsistent sequences we have found from the total number 
# of rows in dat_all_burst
n_inconsistent_sequences <- nrow(dat_decisions_atypical_sequences)
n_after_matching <- nrow(dat_all_burst) - n_inconsistent_sequences
n_consistent_sequences <- nrow(dat_all_burst) - 2*n_inconsistent_sequences
```

* Number of sequences obtained after applying the matching procedure: `r n_after_matching`
* Number of sequences that are inconsistent with study protocol: `r n_inconsistent_sequences`
* Number of sequences that are consistent with study protocol: `r n_consistent_sequences`

```{r}
# Remove these sequence ID's so that, among sequences which are consistent with 
# study protocol, we can ascertain how many of each type there are.
sequence_ids_inconsistent <- c(dat_decisions_atypical_sequences[["paired_with_sequence_id"]], 
                               dat_decisions_atypical_sequences[["stitched_sequence_id"]])
# Now we have a dataset with only those sequences which are consistent with study protocol
dat_burst_consistent_with_protocol <- dat_all_burst %>% 
  filter(!(stitched_sequence_id %in% sequence_ids_inconsistent))
dat_summary <- dat_burst_consistent_with_protocol %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

```{r}
# Remove these sequence ID's so that, among sequences which are consistent with 
# study protocol, we can ascertain how many of each type there are.
sequence_ids_inconsistent <- c(dat_decisions_atypical_sequences[["stitched_sequence_id"]])
# Now we have a dataset with only those sequences which are consistent with study protocol
dat_burst_consistent_with_protocol <- dat_all_burst %>% 
  filter((stitched_sequence_id %in% sequence_ids_inconsistent))
dat_summary <- dat_burst_consistent_with_protocol %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

```{r}
dat_summary <- dat_decisions_atypical_sequences %>%
  group_by(sequence_cat) %>%
  summarise(sequence = unique(sequence_type),
            total = n())
dat_summary[["sequence_cat"]] <- paste("A", dat_summary[["sequence_cat"]], sep = "")

last_row <- data.frame(sequence_cat = NA, 
                       sequence = NA,
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
```

```{r}
knitr::kable(dat_summary)
```

```{r}
dat_summary <- dat_cleaned_burst_with_outside_study_indicator %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

```{r}
# Remove these sequence ID's so that, among sequences which are consistent with 
# study protocol, we can ascertain how many of each type there are.
sequence_ids_inconsistent <- c(dat_decisions_atypical_sequences[["paired_with_sequence_id"]])
# Now we have a dataset with only those sequences which are consistent with study protocol
dat_burst_consistent_with_protocol <- dat_all_burst %>% 
  filter(!(stitched_sequence_id %in% sequence_ids_inconsistent))
dat_summary <- dat_burst_consistent_with_protocol %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

# Phase 2

```{r}
dat_outside <- dat_cleaned_burst_with_outside_study_indicator %>% filter(is_outside_study == 1)
dat_inside <- dat_cleaned_burst_with_outside_study_indicator %>% filter(is_outside_study == 0)
```

## Step: Remove sequences outside of 10-day MRT period

### Outside 10-day MRT Period

```{r}
n_participants <- length(unique(dat_outside[["mars_id"]]))
n_sequences <- nrow(dat_outside)
n_rand <- sum(!is.na(dat_outside[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

```{r}
dat_summary <- dat_outside %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

### Inside 10-day MRT Period

```{r}
n_participants <- length(unique(dat_inside[["mars_id"]]))
n_sequences <- nrow(dat_inside)
n_rand <- sum(!is.na(dat_inside[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

```{r}
dat_summary <- dat_inside %>%
  mutate(is_2qs = if_else(!is.na(ts_2qs_triggered_mountain), 1, 0),
         is_rand = if_else(!is.na(ts_coinflip_mountain), 1, 0),
         is_ema = if_else(!is.na(ts_ema_triggered_mountain), 1, 0)) %>%
  group_by(is_2qs, is_rand, is_ema) %>%
  summarise(total = n()) %>%
  arrange(is_2qs, is_rand, is_ema)

last_row <- data.frame(is_2qs = NA, 
                       is_rand = NA, 
                       is_ema = NA, 
                       total = sum(dat_summary[["total"]]))
dat_summary <- rbind(dat_summary, last_row)
dat_summary[["sequence"]] <- c("S1: Short survey administered (just once), no micro-randomization, no EMA administered",
                               "S2: Short survey administered (just once), micro-randomization (just once), no EMA administered",
                               "S3: Short survey administered (just once), micro-randomization (just once), EMA administered (just once)",
                               "Grand total person-blocks")
dat_summary <- dat_summary %>% select(sequence, everything())
```

```{r}
options(knitr.kable.NA = '')
knitr::kable(dat_summary)
```

## Step: Remove sequences belonging to pilot participants

```{r}
dat_inside_pilot <- dat_inside %>% filter(mars_id %in% mars_ids_pilot)
dat_inside_not_pilot <- dat_inside %>% filter(!(mars_id %in% mars_ids_pilot))
```

### Pilot participants

```{r}
n_participants <- length(unique(dat_inside_pilot[["mars_id"]]))
n_sequences <- nrow(dat_inside_pilot)
n_rand <- sum(!is.na(dat_inside_pilot[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

### Not Pilot participants

```{r}
n_participants <- length(unique(dat_inside_not_pilot[["mars_id"]]))
n_sequences <- nrow(dat_inside_not_pilot)
n_rand <- sum(!is.na(dat_inside_not_pilot[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

## Step: Remove sequences belonging to participants who did not meet EMA completion criteria

```{r}
dat_inside_not_pilot_and_pass <- dat_inside_not_pilot %>% filter(!(mars_id %in% mars_ids_did_not_meet_ema_completion_criteria))
dat_inside_not_pilot_and_fail <- dat_inside_not_pilot %>% filter(mars_id %in% mars_ids_did_not_meet_ema_completion_criteria)
```

### Participants who were not part of the pilot and who met EMA completion criteria

```{r}
n_participants <- length(unique(dat_inside_not_pilot_and_pass[["mars_id"]]))
n_sequences <- nrow(dat_inside_not_pilot_and_pass)
n_rand <- sum(!is.na(dat_inside_not_pilot_and_pass[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

### Participants who were not part of the pilot and who did not meet EMA completion criteria

```{r}
n_participants <- length(unique(dat_inside_not_pilot_and_fail[["mars_id"]]))
n_sequences <- nrow(dat_inside_not_pilot_and_fail)
n_rand <- sum(!is.na(dat_inside_not_pilot_and_fail[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

## Step: remove sequences that fall on the First Day or Last Day of the 10-day MRT

### Sequences on the First Day or Last Day of the 10-day MRT

```{r}
dat_mars_analysis <- dat_matched_to_decision_points %>% 
  filter(!(mars_id %in% mars_ids_excluded_from_all_analytic_datasets)) %>%
  filter((decision_point < 7) | (decision_point > 54))
```


```{r}
n_participants <- length(unique(dat_mars_analysis[["mars_id"]]))
n_sequences <- sum(!is.na(dat_mars_analysis[["ts_2qs_triggered_mountain"]]))
n_rand <- sum(!is.na(dat_mars_analysis[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

### Sequences between the Second and Ninth Day (inclusive) of the 10-day MRT

```{r}
dat_mars_analysis <- dat_matched_to_decision_points %>% 
  filter(!(mars_id %in% mars_ids_excluded_from_all_analytic_datasets)) %>% 
  filter((decision_point >= 7) & (decision_point <= 54))
```


```{r}
n_participants <- length(unique(dat_mars_analysis[["mars_id"]]))
n_sequences <- sum(!is.na(dat_mars_analysis[["ts_2qs_triggered_mountain"]]))
n_rand <- sum(!is.na(dat_mars_analysis[["ts_coinflip_mountain"]]))
```

* Number of participants: `r n_participants`
* Number of sequences: `r n_sequences`
* Number of micro-randomizations: `r n_rand`

